Shifting paradigms in Ocean Color: Bayesian Inference for Uncertainty-Aware Chlorophyll Estimation 

### 2025-05-21 manuscript/manuscript.qmd
updated methods section for model 6

Model 5 - Multi-level hierarchical linear model with partial pooling across $MBR$ numerator groups (Rrs411, Rrs443, Rrs489, Rrs510) for both model mean and model variance.  Model parameter prior mean and variance have Gaussian and Exponential hyperpriors similar to Model 2s.
:::

@@

@@

- **Regression terms**: Normal(0, 1) unless otherwise stated  
- **Hyperpriors**: Normal and HalfNormal for hierarchical parameters  
- **Noise terms** (`σ`): Gamma(γ, φ), chosen to reflect plausible dispersion values

>>>>

Model 5 - Multi-level hierarchical linear model with partial pooling across $MBR$  groups (Rrs411, Rrs443, Rrs489, Rrs510) for both model mean and model variance.  Model parameter prior mean and variance have Gaussian and Exponential hyperpriors similar to Model 2s.
:::

@@

::: {#fig-model6-struct}

![](images/model6_structure.png)

Model 6 - Similar to Model 5; multi-level hierarchical linear model partial pooling across $MBR$  groups (Rrs411, Rrs443, Rrs489, Rrs510) for both model mean and variance. However the linear variance model gets an additional parameter $γ$ that allows for the model dispersion to depend on the chlorophyll measurement method (fluorescence or HPLC). While this doesn't affect future data prediction, for which ground truth mearuement are optional, it does allow the development of insight on the effect of chloroophyll measurement method on model ucertainty.
:::

@@

- **Regression terms**: Normal(0, 1) unless otherwise stated  
- **Hyperpriors**: Normal and Exponential for hierarchical parameters  
- **Noise terms** (`σ`): Gamma(γ, φ), chosen to reflect plausible dispersion values
